---
title: "complementary analysis"
output: html_document
---


```{r,include = FALSE}
library(tidyverse)
library(ggplot2)
library(rstatix)
library(quickpsy)
library(ggpubr)
library(rstatix)
library(lme4)
library(emmeans)
library(gridExtra)
library(psych)
```


#### Analysis in function of the serie presented (across an experimental block)


```{r on accuracy}
### Binomial GLM in function of SNR, age group and serie
model_glm <- glm(cbind(glm_table_perf_children$countval,glm_table_perf_children$countot) ~ SNRdB*serie*grade ,family = binomial(link="logit"), data = glm_table_perf_children)
summary(model_glm)

statsmodelglm = Anova(model_glm,type = 2) # tests stats
print(statsmodelglm, digits = 4)
```

```{r on RTs}
### Inverse gaussian GLM in function of SNR, age group and serie
model_glm <- glm(Trsec ~ SNRdB*serie*grade ,family = inverse.gaussian(link="log"), data = glm_table_all_children)
summary(model_glm)

statsmodelglm = Anova(model_glm,type = 2) # tests stats
print(statsmodelglm, digits = 4)

```
#### Same analysis in function of serie but only with younger children (1st quartile of age)

```{r}
#### We find the first quartile:
print(paste0("the first quartile is ",quantile(age_table$age_in_months, 0.25)/12))

prop_table_time %>%
  subset(age_in_months < 87.25) -> prop_table_time_1st_quart
```
```{r on accuracy}
### Binomial GLM in function of SNR and serie
model_glm <- glm(cbind(prop_table_time_1st_quart$countval,prop_table_time_1st_quart$countot) ~ SNRdB*serie ,family = binomial(link="logit"), data = prop_table_time_1st_quart)
summary(model_glm)

statsmodelglm = Anova(model_glm,type = 2) # tests stats
print(statsmodelglm, digits = 4)
```


```{r on RTs}
glm_table_all_children %>%
  subset(age_in_months < 87.25) -> glm_table_all_children_1st_quart

### Inverse gaussian GLM in function of SNR and serie
model_glm <- glm(Trsec ~ SNRdB*serie ,family = inverse.gaussian(link="log"), data = glm_table_all_children_1st_quart)
summary(model_glm)

statsmodelglm = Anova(model_glm,type = 2) # tests stats
print(statsmodelglm, digits = 4)
```


#### Analysis on RTs in function of the length of target-word on data with only correct trials that are common between easy and difficult conditions

```{r}
raw_data %>%
  subset(grade != "adult" & ans == 1) -> raw_data_correct


final_table = data.frame(matrix(nrow = 0, ncol = length(colnames(raw_data_correct))+1)) 
colnames(final_table) = c(colnames(raw_data_correct),"nb_trials_kept")
for (suj in 1:length(unique(raw_data_correct$ID))){
  for (snr in 1:length(unique(raw_data_correct$SNRdB))){
    raw_data_correct %>%
      subset(ID == unique(raw_data_correct$ID)[suj] & SNRdB == unique(raw_data_correct$SNRdB)[snr]) -> trials
    easy_trials <- subset(trials,difficulty == "easy")
    difficult_trials <- subset(trials,difficulty == "difficult")
    if (nrow(easy_trials) < nrow(difficult_trials)){
       to_keep = difficult_trials[which(difficult_trials$motenvoye %in% easy_trials$motenvoye),"motenvoye"]
    } else{
       to_keep = easy_trials[which(easy_trials$motenvoye %in% difficult_trials$motenvoye),"motenvoye"]
    }
    trials$nb_trials_kept = length(to_keep)
    final_table =  rbind(final_table,trials[which(trials$motenvoye %in% to_keep),])
  }
}

print(paste0("By filtering out the invalid trials, the incorrect trials and keeping only the common words between easy and difficult for each block, we kept ", round(nrow(final_table)/(nrow(unique(raw_data_correct$ID))*48*2)*100,digits = 1), "% of all trials"))
```

```{r}
### Inverse Gaussian GLM model with age group, difficulty, SNR level and target-word length as factors
model_glm <- glm(Trsec ~ grade*difficulty*SNRdB*taillems ,family = inverse.gaussian(link='log'), data = final_table)
summary(model_glm)
statsmodelglm = Anova(model_glm,type = 2) # tests stats
print(statsmodelglm, digits = 4)

#### post-hoc correlations between RTs and post-hoc per age group:
final_table %>%
  select(Trsec,grade,taillems) %>%
  group_by(grade) %>%
  summarise(cor_coeff = cor.test(Trsec,taillems,method = "kendall")$estimate,cor_p = cor.test(Trsec,taillems,method = "kendall")$p.value) -> cor_results
cor_results
```


```{r easy/difficult RT ration in function of the length of the target word}
### normality test on ratio
shapiro.test(unique(glm_ratio_taillems$ratioTR))

### Gaussian GLM on ratio in function of age and length of the target word
model_glm <- glm(ratioTR ~ age_in_months*taillems ,family = gaussian(link='identity'), data = glm_ratio_taillems)
summary(model_glm)

statsmodelglm = Anova(model_glm,type = 2) # tests stats
print(statsmodelglm, digits = 4)

#### Gaussian GLM on ratio in function of log(age) and length of the target word
model_glm <- glm(ratioTR ~ log(age_in_months)*taillems ,family = gaussian(link='identity'), data = glm_ratio_taillems)
summary(model_glm)

statsmodelglm = Anova(model_glm,type = 2) # tests stats
print(statsmodelglm, digits = 4)

### plot of the direction of the evolution of ratio in function of age
glm_ratio_taillems %>%
  group_by(ID,age_in_months) %>%
  summarise(ratioTR = mean(ratioTR)) -> glm_ratio_age

ggplot(data = glm_ratio_age,aes(x = log(log(age_in_months)), y = ratioTR ) ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```

#### Comparison of easy/difficult ratio between older children (5th grade) and adults

```{r comparaison valeur de ratio CM2/adultes}
glm_table_all_correct_common_ratio_ad %>%
  group_by(SNRdB) %>%
  summarise(ratioTR = mean(ratioTR))

glm_table_all_correct_common_ratio_ch %>%
  subset(grade == "CM2") %>%
  group_by(SNRdB) %>%
  summarise(ratioTR = mean(ratioTR))
```

#### Evolution of the difference of accuracy between SNR -3 and SNR +3 as a function of age

```{r}
### from raw data, calculation of the accuracy difference between SNR -3 and SNR +3
glm_table_all %>%
  group_by(ID,grade,SNRdB,difficulty) %>%
  summarise(perf = mean(ans)) %>%
  tidyr::spread(key = SNRdB, value = perf) %>%
  mutate(diffSNR = `3` - `-3`) %>%
  group_by(grade,difficulty) %>%
  summarise(mean_diffSNR = mean(diffSNR),sd_diffSNR = stats::sd(diffSNR,na.rm = T)) %>%
  ungroup()-> diffSNR_table
  diffSNR_table$difficulty = factor(diffSNR_table$difficulty, levels = c("easy","difficult"))

### Figure of the evolution of SNR difference across age group

perf_diffSNR_fig = ggplot(diffSNR_table, aes(x=grade,y=mean_diffSNR, ymin = mean_diffSNR - sd_diffSNR, ymax = mean_diffSNR + sd_diffSNR,fill = difficulty,colour = difficulty)) +
  geom_pointrange(position = position_dodge(0.4)) +
  scale_x_discrete(limits=c("GS","CP","CE1","CE2","CM1","CM2","adult"), labels = c("KG","1st","2nd","3rd","4th","5th","Adults")) +
  ylab(label ="Perf difference between \n SNR +3 and SNR -3") +
  xlab(label="Grades") +
  scale_fill_manual(values=c("#d8b365", "#5ab4ac"),name = "Difficulty", labels = c("Easy","Difficult")) +
    scale_colour_manual(values=c("#d8b365", "#5ab4ac"),name = "Difficulty", labels = c("Easy","Difficult")) +
  #coord_cartesian(ylim = c(0,100)) +
  theme_light() +
  theme_classic()+
  theme(axis.text=element_text(size=18),axis.title=element_text(size=25),legend.text=element_text(size=23),legend.title=element_text(size=25),strip.text.x = element_text(size = 20))
perf_diffSNR_fig

ggsave("perf_diffSNR_fig.png", plot = perf_diffSNR_fig,device = "png",width = 12,height = 7)
```


#### Interclass correlation between series

```{r}
### SNR +3 dB
ICC_table %>%
  subset(SNRdB == "3") %>% 
  ungroup() %>%
  dplyr::select(serie1,serie2,serie3,serie4) -> ICC_matrix_snrp3

icc(ICC_matrix_snrp3, model = "twoway",
  type = "consistency", unit = "average")
ICC(ICC_matrix_snrp3)

### SNR -3 dB
ICC_table %>%
  subset(SNRdB == "-3") %>% 
  ungroup() %>%
  dplyr::select(serie1,serie2,serie3,serie4) -> ICC_matrix_snrm3

icc(ICC_matrix_snrm3, model = "twoway",
  type = "consistency", unit = "average")

ICC(ICC_matrix_snrm3)

```

#### Ranking of performance word and per age group

```{r}
glm_table_all %>%
  subset(dys != 1 & grade != "adult") %>%
  group_by(grade,difficulty,motenvoye) %>%
  summarise(perf = mean(ans)) %>%
  group_by(grade,difficulty) %>%
  mutate(ranked_perf = rank(-perf, ties.method = "first")) -> ranked_perf 

#### easiest words and hardest words for KG children
ranked_perf %>%
  subset(grade == "GS") %>%
  group_by(difficulty) %>%
  summarise(motenvoye_min = motenvoye[which.min(ranked_perf)], motenvoye_max = motenvoye[which.max(ranked_perf)]) 

#### correlation of ranked words between all age groups
ranked_perf %>%
  select(-perf)  %>%
  spread(key = grade, value = ranked_perf) %>% 
  ungroup() %>%
  mutate(mean_ranked = rowMeans(select(.,c(-motenvoye,-difficulty))))-> ranked_perf_for_cor
cor(ranked_perf_for_cor[,c()])


```

